---
title: "The Transgenerational Effect of Environmental Warming on the Upper Thermal Tolerance
of Brook Trout (*S. fontinalis*): Model Selection"
author: "Chantelle M. Penney, Joshua K.R. Tabh, Chris C. Wilson, Gary Burness"
date: "March 22, 2021"
output: html_document
---

```{r warning = FALSE, message = FALSE}

# Directory and Data Import

setwd("/home/joshk/git_repositories/BrookTrout_TG/Data")
BTChallenge <- read.csv("BT Challenge_DegreeDay.csv")

{
  BTChallenge$Offspring.Acc <- as.factor(BTChallenge$Offspring.Acc)
  BTChallenge$Mother.Acc <- as.factor(BTChallenge$Mother.Acc)
  BTChallenge$Father.Acc <- as.factor(BTChallenge$Father.Acc)
  BTChallenge$Mother.ID <- as.factor(BTChallenge$Mother.ID)
  BTChallenge$Father.ID <- as.factor(BTChallenge$Father.ID)
  BTChallenge$Subject.ID <- as.factor(BTChallenge$Subject.ID)
  BTChallenge$Family <- as.factor(BTChallenge$Family)
  BTChallenge$Parent.Group <- as.factor(BTChallenge$Parent.Group)
}

options(na.action = na.omit)

## Loading in necessary packages

library("easypackages")

libraries(
  "broom", "car", "dotwhisker", "dplyr", "ggplot2", "grid",
  "gridExtra", "gtable", "itsadug", "knitr", "lme4", "lmerTest",
  "mgcv", "MuMIn", "nlme", "purrr", "rmarkdown", "splines"
)

# Adding font

library("showtext")
font_add_google(name = "Noto Sans", family = "Noto Sans")

## Additional functions

strip.lme <- function(model.name) {
  coef.names <- c(names(model.name$coefficients$fixed))
  tTab.data <- data.frame(summary(model.name)$tTable[, c(1, 2, 4)], row.names = NULL)
  tTab.data <- cbind(coef.names, tTab.data)
  return(tTab.data)
}

sig.lme <- function(model.name, sig.level = 0.1) {
  sig.data <- as.data.frame(summary(model.name)$tTable[c(which(as.numeric(paste(summary(model.name)$tTable[, 5])) <= sig.level)), ])
  return(sig.data)
}

```
### Assigning ggplot2 themes for figures

```{r warning = FALSE, message = FALSE}

my.theme <- theme(
  panel.grid.minor = element_blank(),
  axis.title = element_text(size = 14, family = "Noto Sans"),
  axis.text = element_text(size = 14, colour = "black", family = "Noto Sans"),
  axis.title.y = element_text(vjust = 0.5), panel.grid.major =
    element_line(colour = "grey75"), legend.title = element_text(
    size = 14,
    colour = "black", family = "Noto Sans"
  ), legend.text = element_text(
    size = 12,
    colour = "black", family = "Noto Sans"
  )
)

my.theme.dw <- theme(
  panel.grid.minor = element_blank(), panel.grid.major = element_blank(),
  axis.title = element_text(size = 12, family = "Noto Sans"),
  axis.text = element_text(size = 12, colour = "black", family = "Noto Sans"),
  legend.title = element_text(
    size = 12,
    colour = "black", family = "Noto Sans"
  ), legend.text = element_text(
    size = 12,
    colour = "black", family = "Noto Sans"
  )
)

my.theme.diag <- theme(
  panel.grid.minor = element_blank(),
  axis.title = element_text(size = 8, family = "Noto Sans"),
  axis.text = element_text(size = 8, colour = "black", family = "Noto Sans"),
  axis.title.y = element_text(angle = 0, vjust = 0.5), panel.grid.major =
    element_line(colour = "grey75"), legend.title = element_text(
    size = 8,
    colour = "black", family = "Noto Sans"
  ), legend.text = element_text(
    size = 8,
    colour = "black", family = "Noto Sans"
  )
)

```
### Assessing parameter distributions by plots

```{r warning = FALSE, message = FALSE}

Unique.Mass <- distinct(BTChallenge, Mass, .keep_all = TRUE) %>%
  select(Subject.ID, Mass, Offspring.Acc, Mother.Acc, Father.Acc, Family)

ggplot(data = Unique.Mass, aes(x = Mass)) +
  geom_histogram(colour = "black", fill = "dodgerblue2", bins = 20) +
  theme_bw() +
  my.theme.diag +
  geom_vline(
    xintercept = with(na.omit(Unique.Mass), mean(Mass)), size = 1.25,
    colour = "black", linetype = "dotted"
  ) +
  xlab("Mass (g)") +
  geom_density(alpha = 0.5, aes(y = 1 / 5 * ..count..), fill = "dodgerblue2")

ggplot(data = Unique.Mass, aes(
  x = Mass, fill = as.factor(Offspring.Acc),
  colour = as.factor(Offspring.Acc)
)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  my.theme.diag +
  geom_vline(
    xintercept = with(na.omit(Unique.Mass), mean(Mass)), size = 1.25,
    colour = "black", linetype = "dotted"
  ) +
  xlab("Mass (g)") +
  geom_density(alpha = 0.5, aes(y = 1 / 4.2 * ..count..)) +
  scale_fill_manual(
    values =
      c("dodgerblue3", "maroon1")
  ) +
  scale_colour_manual(
    values =
      c("black", "black"), guide = FALSE
  ) +
  guides(fill = guide_legend(
    title =
      "Offspring Acclimation \n Temperature"
  ))

## Strong overlap

ggplot(data = Unique.Mass, aes(
  x = Mass, fill = as.factor(Mother.Acc),
  colour = as.factor(Mother.Acc)
)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  my.theme.diag +
  geom_vline(
    xintercept = with(na.omit(Unique.Mass), mean(Mass)), size = 1.25,
    colour = "black", linetype = "dotted"
  ) +
  xlab("Mass (g)") +
  geom_density(alpha = 0.5, aes(y = 2 / 7 * ..count..)) +
  scale_fill_manual(
    values =
      c("slateblue", "lightpink")
  ) +
  scale_colour_manual(
    values =
      c("black", "black"), guide = FALSE
  ) +
  guides(fill = guide_legend(
    title =
      "Maternal Acclimation \n Temperature"
  ))

ggplot(data = Unique.Mass, aes(
  x = Mass, fill = as.factor(Father.Acc),
  colour = as.factor(Father.Acc)
)) +
  geom_histogram(bins = 20) +
  theme_bw() +
  my.theme.diag +
  geom_vline(
    xintercept = with(na.omit(Unique.Mass), mean(Mass)), size = 1.25,
    colour = "black", linetype = "dotted"
  ) +
  xlab("Mass (g)") +
  geom_density(alpha = 0.5, aes(y = 2 / 7 * ..count..)) +
  scale_fill_manual(
    values =
      c("seagreen3", "magenta3")
  ) +
  scale_colour_manual(
    values =
      c("black", "black"), guide = FALSE
  ) +
  guides(fill = guide_legend(
    title =
      "Paternal Acclimation \n Temperature"
  ))

## No obvious distinction between offspring from warm and cold mothers, or fathers.

```
### Exploring metabolic responses to thermal challenge across groupings. Error bars represent +/- 95% CI.

```{r warning = FALSE, message = FALSE}
Challenge.Sum <- BTChallenge %>%
  group_by(Challenge.Temp) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

## All offspring grouped.

ggplot(Challenge.Sum, aes(x = Challenge.Temp, y = Mean)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    color = "dodgerblue3"
  ) +
  geom_point(size = 1, colour = "maroon1") +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)")

# Robust elevation at 25 °C.

Challenge.Sum.Off <- BTChallenge %>%
  group_by(Challenge.Temp, Offspring.Acc) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

## Split by offspring acclimation temperature.

ggplot(as.data.frame(Challenge.Sum.Off), aes(
  x = Challenge.Temp,
  y = Mean, group = Offspring.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("dodgerblue", "maroon1")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature"))

# Some divergence, but does not appear systematic.

Challenge.Sum.Mat <- BTChallenge %>%
  group_by(Challenge.Temp, Mother.Acc) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

# Split by maternal acclimation temperature

ggplot(as.data.frame(Challenge.Sum.Mat), aes(
  x = Challenge.Temp,
  y = Mean, group = Mother.Acc, colour = Mother.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("slateblue", "lightpink")) +
  guides(colour = guide_legend(title = "Maternal Acclimation \n Temperature"))

# Perhaps a very subtle divergence.

Challenge.Sum.Pat <- BTChallenge %>%
  group_by(Challenge.Temp, Father.Acc) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

# Split by Paternal Acclimation Temperature.

ggplot(as.data.frame(Challenge.Sum.Pat), aes(
  x = Challenge.Temp,
  y = Mean, group = Father.Acc, colour = Father.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("seagreen3", "magenta3")) +
  guides(colour = guide_legend(title = "Paternal Acclimation \n Temperature"))

# Subtle effect at upper temperatures.

Challenge.Sum.OffMat <- BTChallenge %>%
  group_by(Challenge.Temp, Offspring.Acc, Mother.Acc) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

OffMat.Group <- c()
for (i in 1:nrow(Challenge.Sum.OffMat)) {
  if (Challenge.Sum.OffMat$Offspring.Acc[i] == 1 & Challenge.Sum.OffMat$Mother.Acc[i] == 1) {
    OffMat.Group[i] <- ("1")
  } else if (
    Challenge.Sum.OffMat$Offspring.Acc[i] == 1 & Challenge.Sum.OffMat$Mother.Acc[i] == 2) {
    OffMat.Group[i] <- ("2")
  } else if (
    Challenge.Sum.OffMat$Offspring.Acc[i] == 2 & Challenge.Sum.OffMat$Mother.Acc[i] == 1) {
    OffMat.Group[i] <- ("3")
  } else if (
    Challenge.Sum.OffMat$Offspring.Acc[i] == 2 & Challenge.Sum.OffMat$Mother.Acc[i] == 2) {
    OffMat.Group[i] <- ("4")
  }
}

Challenge.Sum.OffMat$OffMat <- OffMat.Group

# Parsing by Maternal and Offspring Acclimation Temperature

ggplot(as.data.frame(Challenge.Sum.OffMat), aes(
  x = Challenge.Temp,
  y = Mean, group = OffMat, shape = Mother.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("black", "gold2")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Maternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

Challenge.Sum.OffPat <- BTChallenge %>%
  group_by(Challenge.Temp, Offspring.Acc, Father.Acc) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

OffPat.Group <- c()
for (i in 1:nrow(Challenge.Sum.OffPat)) {
  if (Challenge.Sum.OffPat$Offspring.Acc[i] == 1 & Challenge.Sum.OffPat$Father.Acc[i] == 1) {
    OffPat.Group[i] <- ("1")
  } else if (
    Challenge.Sum.OffPat$Offspring.Acc[i] == 1 & Challenge.Sum.OffPat$Father.Acc[i] == 2) {
    OffPat.Group[i] <- ("2")
  } else if (
    Challenge.Sum.OffPat$Offspring.Acc[i] == 2 & Challenge.Sum.OffPat$Father.Acc[i] == 1) {
    OffPat.Group[i] <- ("3")
  } else if (
    Challenge.Sum.OffPat$Offspring.Acc[i] == 2 & Challenge.Sum.OffPat$Father.Acc[i] == 2) {
    OffPat.Group[i] <- ("4")
  }
}

# Now parsing by paternal and offspring acclimation temperatures

Challenge.Sum.OffPat$OffPat <- OffPat.Group
ggplot(as.data.frame(Challenge.Sum.OffPat), aes(
  x = Challenge.Temp,
  y = Mean, group = OffPat, shape = Father.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("dodgerblue3", "maroon1")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Paternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

# Possible, subtle interaction.

```
### Producing three-way "interaction" plots
```{r warning = FALSE, message = FALSE}
Challenge.Sum.All <- BTChallenge %>%
  group_by(Challenge.Temp, Offspring.Acc, Father.Acc, Mother.Acc) %>%
  summarize(
    Mean = mean(MO2.NMS, na.rm = TRUE), Upper.CI = mean(MO2.NMS,
      na.rm = TRUE
    ) + 1.96 * (sd(MO2.NMS, na.rm = TRUE) / sqrt(length(na.omit(MO2.NMS)))),
    Lower.CI = mean(MO2.NMS, na.rm = TRUE) - 1.96 * (sd(MO2.NMS, na.rm = TRUE) /
      sqrt(length(na.omit(MO2.NMS))))
  )

OffPat.Group.All <- c()
for (i in 1:nrow(Challenge.Sum.All)) {
  if (Challenge.Sum.All$Offspring.Acc[i] == 1 &
    Challenge.Sum.All$Father.Acc[i] == 1) {
    OffPat.Group.All[i] <- ("1")
  } else if (
    Challenge.Sum.All$Offspring.Acc[i] == 1 &
      Challenge.Sum.All$Father.Acc[i] == 2) {
    OffPat.Group.All[i] <- ("2")
  } else if (
    Challenge.Sum.All$Offspring.Acc[i] == 2 &
      Challenge.Sum.All$Father.Acc[i] == 1) {
    OffPat.Group.All[i] <- ("3")
  } else if (
    Challenge.Sum.All$Offspring.Acc[i] == 2 &
      Challenge.Sum.All$Father.Acc[i] == 2) {
    OffPat.Group.All[i] <- ("4")
  }
}
Challenge.Sum.All$OffPat <- OffPat.Group.All

OffMat.Group.All <- c()
for (i in 1:nrow(Challenge.Sum.All)) {
  if (Challenge.Sum.All$Offspring.Acc[i] == 1 &
    Challenge.Sum.All$Mother.Acc[i] == 1) {
    OffMat.Group.All[i] <- ("1")
  } else if (
    Challenge.Sum.All$Offspring.Acc[i] == 1 &
      Challenge.Sum.All$Mother.Acc[i] == 2) {
    OffMat.Group.All[i] <- ("2")
  } else if (
    Challenge.Sum.All$Offspring.Acc[i] == 2 &
      Challenge.Sum.All$Mother.Acc[i] == 1) {
    OffMat.Group.All[i] <- ("3")
  } else if (
    Challenge.Sum.All$Offspring.Acc[i] == 2 &
      Challenge.Sum.All$Mother.Acc[i] == 2) {
    OffMat.Group.All[i] <- ("4")
  }
}
Challenge.Sum.All$OffMat <- OffMat.Group.All

MatPat.Group.All <- c()
for (i in 1:nrow(Challenge.Sum.All)) {
  if (Challenge.Sum.All$Mother.Acc[i] == 1 &
    Challenge.Sum.All$Father.Acc[i] == 1) {
    MatPat.Group.All[i] <- ("1")
  } else if (
    Challenge.Sum.All$Mother.Acc[i] == 1 &
      Challenge.Sum.All$Father.Acc[i] == 2) {
    MatPat.Group.All[i] <- ("2")
  } else if (
    Challenge.Sum.All$Mother.Acc[i] == 2 &
      Challenge.Sum.All$Father.Acc[i] == 1) {
    MatPat.Group.All[i] <- ("3")
  } else if (
    Challenge.Sum.All$Mother.Acc[i] == 2 &
      Challenge.Sum.All$Father.Acc[i] == 2) {
    MatPat.Group.All[i] <- ("4")
  }
}
Challenge.Sum.All$MatPat <- MatPat.Group.All

OffParError.DFacet <- ggplot(as.data.frame(Challenge.Sum.All), aes(
  x = Challenge.Temp,
  y = Mean, group = OffPat, shape = Father.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("dodgerblue3", "maroon1")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Paternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

## Facetting by maternal acclimation temperature first

OffParError.DFacet + facet_grid(rows = vars(Mother.Acc))

OffParError.SFacet <- ggplot(as.data.frame(Challenge.Sum.All), aes(
  x = Challenge.Temp,
  y = Mean, group = OffMat, shape = Mother.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("slateblue", "gold2")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Maternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

## Now facetting by paternal acclimation temperature

OffParError.SFacet + facet_grid(rows = vars(Father.Acc))

ParError.OFacet <- ggplot(as.data.frame(Challenge.Sum.All), aes(
  x = Challenge.Temp,
  y = Mean, group = MatPat, shape = Mother.Acc, colour = Father.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("mediumseagreen", "mediumorchid")) +
  guides(colour = guide_legend(title = "Paternal Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Maternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

## And lastly, facetting by offspring acclimation temperature

ParError.OFacet + facet_grid(rows = vars(Offspring.Acc))

```

### Model construction

```{r warning = FALSE, message = FALSE}

## Building cubic regression spline with low edf (here, 4) due to low curvature. Fitting spline to global data.

plot(MO2.NMS ~ Challenge.Temp, data = na.omit(BTChallenge))
curve.model <- gam(MO2.NMS ~ s(Challenge.Temp, bs = "cs", k = 7), na.action = na.exclude, data = BTChallenge)

## Results of gam
summary(curve.model)
plot(curve.model)

# Appears nicely fitting.

## Pulling out predicted values

smoother <- predict(curve.model, type = "response")

With.Fit <- BTChallenge
With.Fit$MO2.NMS <- smoother
With.Fit <- With.Fit %>%
  mutate("Type" = "Fit")
Resp.Alone <- BTChallenge
Resp.Alone$Type <- "Response"
Total.Data <- rbind(With.Fit, Resp.Alone)

## Plotting the cubic regression spline

Total.Data %>%
  ggplot(aes(x = Challenge.Temp, y = MO2.NMS, fill = Type, linetype = Type)) +
  geom_point(pch = 21) +
  scale_fill_manual(values = c("black", "magenta")) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cr", k = 7))

## Again, appears fitting. Appending spline to dataframe

BTChallenge$bSpline <- smoother

# Constructing linear model
## Crossed random intercepts per parental ID, with crossed Offspring ID.

BTChallenge <- BTChallenge %>%
  dplyr::rename("Degree.Day" = Degree.Dat)

BTChallenge$Degree.Day <- factor(BTChallenge$Degree.Day)
Dummy <- factor(1)
Dat <- groupedData(MO2.NMS ~ 1 | Dummy, BTChallenge)

Model1 <- lme(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc, random = pdBlocked(list(pdIdent(~ 0 + Father.ID), pdIdent(~ 0 + Mother.ID), pdIdent(~ 0 + Subject.ID), pdIdent(~ 0 + Degree.Day))), na.action = na.exclude, data = Dat)

# Assuming large degrees of freedom by estimating Z values (using glmmTMB):

require("glmmTMB")

Model1TMB <- glmmTMB(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc + (1 | Father.ID) + (1 | Mother.ID) + (1 | Subject.ID) + (1 | Degree.Day), na.action = na.exclude, data = BTChallenge)

# Diagnosing residuals

{
  M1.Res.Alone <- ggplot(
    data = data.frame("Res" = residuals(Model1, type = "normalized")),
    aes(x = 1:nrow(Dat), y = Res)
  ) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumseagreen", alpha = 0.5) +
    xlab("Row Number") +
    ylab("Deviance Residuals")

  M1.Res.by.Fit <- ggplot(data = data.frame(
    "Res" = residuals(Model1, type = "normalized"),
    "Fit" = predict(Model1)
  ), aes(x = Fit, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "cornflowerblue", alpha = 0.5) +
    xlab("Fitted Values") +
    ylab("Deviance Residuals")

  M1.Res.by.Resp <- ggplot(data = data.frame(
    "Res" = residuals(Model1, type = "normalized"),
    "Resp" = Dat$MO2.NMS
  ), aes(x = Resp, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumorchid", alpha = 0.5) +
    xlab("Metabolic Rate (mg O2/hour") +
    ylab("Deviance Residuals")

  M1.QQNorm.1 <- ggplot(
    data.frame("Res" = residuals(Model1), "Fit" = predict(Model1)),
    aes(sample = Res)
  ) +
    stat_qq(colour = "gold") +
    stat_qq_line() +
    my.theme +
    theme_bw()
}

grid.arrange(M1.Res.Alone, M1.Res.by.Fit, M1.Res.by.Resp, M1.QQNorm.1, nrow = 2, top = "Metabolic Rate Residuals")

# Large df

{
  M1.Res.Alone.z <- ggplot(
    data = data.frame("Res" = residuals(Model1TMB, type = "pearson")),
    aes(x = 1:nrow(BTChallenge), y = Res)
  ) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumseagreen", alpha = 0.5) +
    xlab("Row Number") +
    ylab("Pearson Residuals")

  M1.Res.by.Fit.z <- ggplot(data = data.frame(
    "Res" = residuals(Model1TMB, type = "pearson"),
    "Fit" = predict(Model1)
  ), aes(x = Fit, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "cornflowerblue", alpha = 0.5) +
    xlab("Fitted Values") +
    ylab("Pearson Residuals")

  M1.Res.by.Resp.z <- ggplot(data = data.frame(
    "Res" = residuals(Model1TMB, type = "pearson"),
    "Resp" = BTChallenge$MO2.NMS
  ), aes(x = Resp, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumorchid", alpha = 0.5) +
    xlab("Metabolic Rate (mg O2/hour") +
    ylab("Pearson Residuals")

  M1.QQNorm.1.z <- ggplot(
    data.frame("Res" = residuals(Model1TMB), "Fit" = predict(Model1TMB)),
    aes(sample = Res)
  ) +
    stat_qq(colour = "gold") +
    stat_qq_line() +
    my.theme +
    theme_bw()
}

grid.arrange(M1.Res.Alone.z, M1.Res.by.Fit.z, M1.Res.by.Resp.z, M1.QQNorm.1.z, nrow = 2, top = "Metabolic Rate Residuals")

## T model: Straying from normality in upper quantiles. Fan notable in residuals by fitteds. Perhaps weight by challenge temperature. First, testing for autocorrelation.
## Z model: Bias in residuals. Very well could be a consequence of autocorrelation.

ggplot(with(
  acf(na.omit(residuals(Model1, type = "normalized")), plot = "FALSE"),
  data.frame(lag, acf)
), aes(x = lag, y = acf)) +
  geom_bar(
    stat = "identity",
    position = "identity", fill = "slateblue", colour = "black"
  ) +
  theme_bw() +
  my.theme.diag +
  ylab("Autocorrelation \n Factor")
rho <- acf(na.omit(residuals(Model1, type = "normalized")), plot = F)$acf[2]
print(rho)

ggplot(with(
  acf(na.omit(residuals(Model1TMB, type = "pearson")), plot = "FALSE"),
  data.frame(lag, acf)
), aes(x = lag, y = acf)) +
  geom_bar(
    stat = "identity",
    position = "identity", fill = "slateblue", colour = "black"
  ) +
  theme_bw() +
  my.theme.diag +
  ylab("Autocorrelation \n Factor")
rho <- acf(na.omit(residuals(Model1, type = "normalized")), plot = F)$acf[2]
print(rho)

# Minor autocorrelation between measures in both models model. Estimating rho.
# Faceting by paternal acclimation temperature for clearer viewing.

Dat %>%
  mutate("Res" = residuals(Model1, type = "normalized")) %>%
  ggplot(aes(x = 1:nrow(Dat), y = Res, fill = Subject.ID, colour = Subject.ID)) +
  my.theme +
  theme_bw() +
  geom_point(
    size = 1, colour = "mediumseagreen",
    alpha = 0.5, pch = 21
  ) +
  xlab("Row Number") +
  ylab("Deviance Residuals") +
  theme(legend.position = "NULL") +
  geom_line(alpha = 0.4) +
  facet_grid(
    rows =
      Dat$Father.Acc
  )

Dat %>%
  mutate("Res" = residuals(Model1TMB, type = "pearson")) %>%
  ggplot(aes(x = 1:nrow(Dat), y = Res, fill = Subject.ID, colour = Subject.ID)) +
  my.theme +
  theme_bw() +
  geom_point(
    size = 1, colour = "mediumseagreen",
    alpha = 0.5, pch = 21
  ) +
  xlab("Row Number") +
  ylab("Pearson Residuals") +
  theme(legend.position = "NULL") +
  geom_line(alpha = 0.4) +
  facet_grid(
    rows =
      Dat$Father.Acc
  )

## Similar lag to models in Penney et al (In Press). Residuals, however, appear evenly spread.

# Adjusting for autocorrelation.

Model.AR <- lme(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc, random = pdBlocked(list(pdIdent(~ 0 + Father.ID), pdIdent(~ 0 + Mother.ID), pdIdent(~ 0 + Subject.ID), pdIdent(~ 0 + Degree.Day))), correlation = corAR1(), na.action = na.exclude, data = Dat)

BTChallenge$AR_Group <- factor(with(BTChallenge, paste(Father.ID, Mother.ID, Subject.ID, sep = "_")))
BTChallenge <- BTChallenge %>%
  mutate("Time" = Challenge.Temp - 14) %>%
  mutate("Time" = factor(Time)) %>%
  arrange(AR_Group, Time) %>%
  as.data.frame(.)

ModelTMB.AR <- glmmTMB(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc + (1 | Father.ID) + (1 | Mother.ID) + (1 | Subject.ID) + (1 | Degree.Day) + ar1(Time + 0 | AR_Group), na.action = na.exclude, data = BTChallenge)

## Diagnostics again.
# T-model

{
  MAR.Res.Alone <- ggplot(data = data.frame("Res" = residuals(Model.AR,
    type =
      "normalized"
  )), aes(x = 1:nrow(Dat), y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumseagreen", alpha = 0.5) +
    xlab("Row Number") +
    ylab("Deviance Residuals")

  MAR.Res.by.Fit <- ggplot(data = data.frame("Res" = residuals(Model.AR,
    type =
      "normalized"
  ), "Fit" = predict(Model.AR)), aes(x = Fit, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "cornflowerblue", alpha = 0.5) +
    xlab("Fitted Values") +
    ylab("Deviance Residuals")

  MAR.Res.by.Resp <- ggplot(data = data.frame("Res" = residuals(Model.AR,
    type =
      "normalized"
  ), "Resp" = Dat$MO2.NMS), aes(x = Resp, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumorchid", alpha = 0.5) +
    xlab("Metabolic Rate (mg O2/hour") +
    ylab("Deviance Residuals")

  MAR.QQNorm.1 <- ggplot(
    data.frame("Res" = residuals(Model.AR), "Fit" = predict(Model.AR)),
    aes(sample = Res)
  ) +
    stat_qq(colour = "gold") +
    stat_qq_line() +
    my.theme +
    theme_bw()
}

grid.arrange(MAR.Res.Alone, MAR.Res.by.Fit, MAR.Res.by.Resp, MAR.QQNorm.1, nrow = 2, top = "Metabolic Rate Residuals - Autoregressive Correlation Structure")

# Z-model

{
  MAR.Res.Alone.z <- ggplot(data = data.frame("Res" = residuals(ModelTMB.AR,
    type =
      "response"
  )), aes(x = 1:nrow(BTChallenge), y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumseagreen", alpha = 0.5) +
    xlab("Row Number") +
    ylab("Response Residuals")

  MAR.Res.by.Fit.z <- ggplot(data = data.frame("Res" = residuals(ModelTMB.AR,
    type =
      "response"
  ), "Fit" = predict(ModelTMB.AR)), aes(x = Fit, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "cornflowerblue", alpha = 0.5) +
    xlab("Fitted Values") +
    ylab("Response Residuals")

  MAR.Res.by.Resp.z <- ggplot(data = data.frame("Res" = residuals(ModelTMB.AR,
    type =
      "response"
  ), "Resp" = BTChallenge$MO2.NMS), aes(x = Resp, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumorchid", alpha = 0.5) +
    xlab("Metabolic Rate (mg O2/hour") +
    ylab("Response Residuals")

  MAR.QQNorm.1.z <- ggplot(
    data.frame("Res" = residuals(ModelTMB.AR), "Fit" = predict(ModelTMB.AR)),
    aes(sample = Res)
  ) +
    stat_qq(colour = "gold") +
    stat_qq_line() +
    my.theme +
    theme_bw()
}

grid.arrange(MAR.Res.Alone.z, MAR.Res.by.Fit.z, MAR.Res.by.Resp.z, MAR.QQNorm.1.z, nrow = 2, top = "Metabolic Rate Residuals - Autoregressive Correlation Structure")

# Very similar outcome to previous models. In glmmTMB model, similarities could merely be a consequence of plotted residuals not correcting for autocorrelation. Checking

plot(residuals(ModelTMB.AR, type = "response") ~ residuals(Model1TMB, type = "response"))
plot(residuals(ModelTMB.AR, type = "pearson") ~ residuals(Model1TMB, type = "pearson"))

# Yes, this appears to be the case. Using DHARMa to assess residuals

require("DHARMa")
BTChallenge_Clean <- na.omit(BTChallenge)
BTChallenge_Clean$Time_Int <- as.integer(BTChallenge_Clean$Time)

ModelTMB.AR <- glmmTMB(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc + (1 | Father.ID) + (1 | Mother.ID) + (1 | Subject.ID) + (1 | Degree.Day) + ar1(Time + 0 | AR_Group), na.action = na.omit, data = BTChallenge_Clean)

dharma_resid <- simulateResiduals(fittedModel = ModelTMB.AR)
plotResiduals(dharma_resid, quantreg = T) # Yes, residuals already appear cleaner.
dharma_residAR <- recalculateResiduals(dharma_resid, group = BTChallenge_Clean$Time)
testTemporalAutocorrelation(simulationOutput = dharma_residAR, time = sort(unique(BTChallenge_Clean$Time)))

ggplot(with(
  acf(na.omit(residuals(Model.AR, type = "normalized")), plot = "FALSE"),
  data.frame(lag, acf)
), aes(x = lag, y = acf)) +
  geom_bar(
    stat = "identity",
    position = "identity", fill = "slateblue", colour = "black"
  ) +
  theme_bw() +
  my.theme.diag +
  ylab("Autocorrelation \n Factor")

## Yes, autocorrelation and residuals do appear okay in both models.
# Again, faceting by paternal acclimation temperature for clearer viewing.

Dat %>%
  mutate("Res" = residuals(Model.AR, type = "normalized")) %>%
  ggplot(aes(x = 1:nrow(Dat), y = Res, fill = Subject.ID, colour = Subject.ID)) +
  my.theme +
  theme_bw() +
  geom_point(
    size = 1, colour = "mediumseagreen",
    alpha = 0.5, pch = 21
  ) +
  xlab("Row Number") +
  ylab("Deviance Residuals") +
  theme(legend.position = "NULL") +
  geom_line(alpha = 0.4) +
  facet_grid(
    rows =
      Dat$Father.Acc
  )

BTChallenge_Clean %>%
  mutate("Res" = dharma_resid$scaledResiduals) %>%
  ggplot(aes(x = 1:nrow(BTChallenge_Clean), y = Res, fill = Subject.ID, colour = Subject.ID)) +
  my.theme +
  theme_bw() +
  geom_point(
    size = 1, colour = "mediumseagreen",
    alpha = 0.5, pch = 21
  ) +
  xlab("Row Number") +
  ylab("Deviance Residuals") +
  theme(legend.position = "NULL") +
  geom_line(alpha = 0.4) +
  facet_grid(
    rows =
      BTChallenge_Clean$Father.Acc
  )

# Good.

## Addressing tail in residuals

Dat %>%
  mutate("Res" = residuals(Model1, type = "normalized"), "Fit" = predict(Model.AR)) %>%
  ggplot(aes(sample = Res, fill = Challenge.Temp)) +
  geom_qq(pch = 21, size = 3, alpha = 0.5, aes(fill = factor(Dat$Challenge.Temp))) +
  stat_qq_line() +
  my.theme +
  theme_bw()

G_Col <- c(Cold = "dodgerblue3", Warm = "gold2", Hot = "firebrick")
Dat %>%
  mutate("Res" = abs(residuals(Model1, type = "normalized"))) %>%
  mutate("Temp_Group" = ifelse(Challenge.Temp < 20, "Cold",
    ifelse(Challenge.Temp > 25, "Hot", "Warm")
  )) %>%
  mutate("Temp_Group" = factor(Temp_Group, levels = c("Cold", "Warm", "Hot"))) %>%
  ggplot(aes(x = Res, fill = Temp_Group)) +
  geom_density(alpha = 0.4, colour = "black", adjust = 2) +
  scale_fill_manual(values = G_Col) +
  theme_classic()

BTChallenge_Clean %>%
  mutate("Res" = dharma_resid$scaledResiduals) %>%
  mutate("Temp_Group" = ifelse(Challenge.Temp < 20, "Cold",
    ifelse(Challenge.Temp > 25, "Hot", "Warm")
  )) %>%
  mutate("Temp_Group" = factor(Temp_Group, levels = c("Cold", "Warm", "Hot"))) %>%
  ggplot(aes(x = Res, fill = Temp_Group)) +
  geom_density(alpha = 0.4, colour = "black", adjust = 2) +
  scale_fill_manual(values = G_Col) +
  theme_classic()

# Slightly disproportionate pulling in cold and warm groups. Weighting by challenge temperature

Model.AR2 <- lme(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc, random = pdBlocked(list(pdIdent(~ 0 + Father.ID), pdIdent(~ 0 + Mother.ID), pdIdent(~ 0 + Subject.ID), pdIdent(~ 0 + Degree.Day))), correlation = corAR1(), weights = ~ 1 / Challenge.Temp, na.action = na.exclude, data = Dat)

ModelTMB2.AR <- glmmTMB(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc + (1 | Father.ID) + (1 | Mother.ID) + (1 | Subject.ID) + (1 | Degree.Day) + ar1(Time + 0 | AR_Group), weights = 1 / Challenge.Temp, na.action = na.omit, data = BTChallenge_Clean)

# glmmTMB model failing to converge. Assessing residuals of lme model.

{
  MAR2.Res.Alone <- ggplot(data = data.frame("Res" = residuals(Model.AR2,
    type =
      "normalized"
  )), aes(x = 1:nrow(Dat), y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumseagreen", alpha = 0.5) +
    xlab("Row Number") +
    ylab("Deviance Residuals")

  MAR2.Res.by.Fit <- ggplot(data = data.frame("Res" = residuals(Model.AR2,
    type =
      "normalized"
  ), "Fit" = predict(Model.AR2)), aes(x = Fit, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "cornflowerblue", alpha = 0.5) +
    xlab("Fitted Values") +
    ylab("Deviance Residuals")

  MAR2.Res.by.Resp <- ggplot(data = data.frame("Res" = residuals(Model.AR2,
    type =
      "normalized"
  ), "Resp" = Dat$MO2.NMS), aes(x = Resp, y = Res)) +
    my.theme +
    theme_bw() +
    geom_point(size = 3, colour = "mediumorchid", alpha = 0.5) +
    xlab("Metabolic Rate (mg O2/hour") +
    ylab("Deviance Residuals")

  MAR2.QQNorm <- ggplot(data.frame("Res" = residuals(Model.AR2, type = "normalized"), "Fit" = predict(Model.AR2)), aes(sample = Res)) +
    stat_qq(colour = "gold") +
    stat_qq_line() +
    my.theme +
    theme_bw()
}

grid.arrange(MAR2.Res.Alone, MAR2.Res.by.Fit, MAR2.Res.by.Resp, MAR2.QQNorm, nrow = 2, top = "Metabolic Rate Residuals - Autoregressive Correlation Structure and Weighted by Challenge Temp.")

## Tail persisting, but subtly. Plotting histogram of residuals.

Dat %>%
  mutate("Res" = residuals(Model.AR2, type = "normalized")) %>%
  ggplot(aes(x = Res)) +
  geom_histogram(fill = "magenta", colour = "black", size = 1, bins = 20) +
  xlab("Normalized Residuals")

## Appears quite nice, though a few notable outliers. Identifying outliers.

Dat <- Dat %>%
  mutate("Res" = residuals(Model.AR2, type = "normalized"))

Grouped <- rbind(subset(Dat, Res < with(na.omit(Dat), mean(Res) - 3 * sd(Res))) %>%
  mutate("Res.Group" = "Low.Out"), subset(Dat, Res > with(na.omit(Dat), mean(Res) + 3 * sd(Res))) %>%
  mutate("Res.Group" = "High.Out"), subset(Dat, Res >= with(na.omit(Dat), mean(Res) - 3 * sd(Res)) & Res <= with(na.omit(Dat), mean(Res) + 3 * sd(Res))) %>%
  mutate("Res.Group" = "Normal"))

G1 <- data.frame(subset(Grouped, Res.Group == "High.Out") %>%
  count(Offspring.Acc), "Group" = "Offspring.Acc")
colnames(G1) <- c("Group.Number", "Count", "Group")

G2 <- data.frame(subset(Grouped, Res.Group == "High.Out") %>%
  count(Father.Acc), "Group" = "Father.Acc")
colnames(G2) <- c("Group.Number", "Count", "Group")

G3 <- data.frame(subset(Grouped, Res.Group == "High.Out") %>%
  count(Mother.Acc), "Group" = "Mother.Acc")
colnames(G3) <- c("Group.Number", "Count", "Group")

rbind(G1, G2, G3)

## Possible interactive assortment. Checking below.

subset(Grouped, Res.Group == "High.Out") %>%
  count(Father.Acc:Mother.Acc)

## Not distinct. Checking trends accross acclimation temperature

subset(Grouped, Res.Group == "High.Out") %>%
  count(Challenge.Temp)

## Not clear either. Residual trends do not appear systematic. Continuing with previous model as final.

```
### Plotting Predicted Values

```{r warning = FALSE, message = FALSE}

Dat$Pred <- predict(Model.AR)

Challenge.Sum.Pred <- Dat %>%
  group_by(Challenge.Temp, Offspring.Acc, Father.Acc, Mother.Acc) %>%
  summarize(
    Mean = mean(Pred, na.rm = TRUE), Upper.CI = mean(Pred,
      na.rm = TRUE
    ) + 1.96 * (sd(Pred, na.rm = TRUE) / sqrt(length(na.omit(Pred)))),
    Lower.CI = mean(Pred, na.rm = TRUE) - 1.96 * (sd(Pred, na.rm = TRUE) /
      sqrt(length(na.omit(Pred))))
  )

OffPat.Group.Pred <- c()
for (i in 1:nrow(Challenge.Sum.Pred)) {
  if (Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
    Challenge.Sum.Pred$Father.Acc[i] == 1) {
    OffPat.Group.Pred[i] <- ("1")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
      Challenge.Sum.Pred$Father.Acc[i] == 2) {
    OffPat.Group.Pred[i] <- ("2")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Father.Acc[i] == 1) {
    OffPat.Group.Pred[i] <- ("3")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Father.Acc[i] == 2) {
    OffPat.Group.Pred[i] <- ("4")
  }
}
Challenge.Sum.Pred$OffPat <- OffPat.Group.Pred

# Faceting by maternal acclimation temperature.

PredError <- ggplot(as.data.frame(Challenge.Sum.Pred), aes(
  x = Challenge.Temp,
  y = Mean, group = OffPat, shape = Father.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("dodgerblue3", "maroon1")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Paternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

PredError + facet_grid(rows = vars(Mother.Acc))

OffMat.Group.Pred <- c()
for (i in 1:nrow(Challenge.Sum.Pred)) {
  if (Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
    Challenge.Sum.Pred$Mother.Acc[i] == 1) {
    OffMat.Group.Pred[i] <- ("1")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
      Challenge.Sum.Pred$Mother.Acc[i] == 2) {
    OffMat.Group.Pred[i] <- ("2")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Mother.Acc[i] == 1) {
    OffMat.Group.Pred[i] <- ("3")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Mother.Acc[i] == 2) {
    OffMat.Group.Pred[i] <- ("4")
  }
}

Challenge.Sum.Pred$OffMat <- OffMat.Group.Pred

# And faceting by paternal acclimation temperature

PredError <- ggplot(as.data.frame(Challenge.Sum.Pred), aes(
  x = Challenge.Temp,
  y = Mean, group = OffMat, shape = Mother.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("cornflowerblue", "gold2")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Maternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

PredError + facet_grid(rows = vars(Father.Acc))

## Striking model fit. Checking glmmTMB model

BTChallenge_Clean$Pred <- predict(ModelTMB.AR)

Challenge.Sum.Pred <- BTChallenge_Clean %>%
  group_by(Challenge.Temp, Offspring.Acc, Father.Acc, Mother.Acc) %>%
  summarize(
    Mean = mean(Pred, na.rm = TRUE), Upper.CI = mean(Pred,
      na.rm = TRUE
    ) + 1.96 * (sd(Pred, na.rm = TRUE) / sqrt(length(na.omit(Pred)))),
    Lower.CI = mean(Pred, na.rm = TRUE) - 1.96 * (sd(Pred, na.rm = TRUE) /
      sqrt(length(na.omit(Pred))))
  )

OffPat.Group.Pred <- c()
for (i in 1:nrow(Challenge.Sum.Pred)) {
  if (Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
    Challenge.Sum.Pred$Father.Acc[i] == 1) {
    OffPat.Group.Pred[i] <- ("1")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
      Challenge.Sum.Pred$Father.Acc[i] == 2) {
    OffPat.Group.Pred[i] <- ("2")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Father.Acc[i] == 1) {
    OffPat.Group.Pred[i] <- ("3")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Father.Acc[i] == 2) {
    OffPat.Group.Pred[i] <- ("4")
  }
}
Challenge.Sum.Pred$OffPat <- OffPat.Group.Pred

# Faceting by maternal acclimation temperature again.

PredError <- ggplot(as.data.frame(Challenge.Sum.Pred), aes(
  x = Challenge.Temp,
  y = Mean, group = OffPat, shape = Father.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("dodgerblue3", "maroon1")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Paternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

PredError + facet_grid(rows = vars(Mother.Acc))

OffMat.Group.Pred <- c()
for (i in 1:nrow(Challenge.Sum.Pred)) {
  if (Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
    Challenge.Sum.Pred$Mother.Acc[i] == 1) {
    OffMat.Group.Pred[i] <- ("1")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 1 &
      Challenge.Sum.Pred$Mother.Acc[i] == 2) {
    OffMat.Group.Pred[i] <- ("2")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Mother.Acc[i] == 1) {
    OffMat.Group.Pred[i] <- ("3")
  } else if (
    Challenge.Sum.Pred$Offspring.Acc[i] == 2 &
      Challenge.Sum.Pred$Mother.Acc[i] == 2) {
    OffMat.Group.Pred[i] <- ("4")
  }
}

Challenge.Sum.Pred$OffMat <- OffMat.Group.Pred

# Paternal acclimation temperature?

PredError <- ggplot(as.data.frame(Challenge.Sum.Pred), aes(
  x = Challenge.Temp,
  y = Mean, group = OffMat, shape = Mother.Acc, colour = Offspring.Acc
)) +
  theme_bw() +
  my.theme +
  geom_errorbar(
    mapping = aes(
      x = Challenge.Temp,
      ymin = c(Lower.CI), ymax = c(Upper.CI)
    ), width = 0.2, size = 1,
    position = position_dodge(width = 0.5)
  ) +
  geom_point(size = 1.5, colour = "black", position = position_dodge(width = 0.5)) +
  xlab("Challenge Temperature \n (°C)") +
  ylab("Metabolic Rate (mg O2/h)") +
  theme(legend.position = "top") +
  scale_colour_manual(values = c("cornflowerblue", "gold2")) +
  guides(colour = guide_legend(title = "Offspring Acclimation \n Temperature")) +
  guides(shape = guide_legend(title = "Maternal Acclimation \n Temperature")) +
  theme(legend.title = element_text(size = 10))

PredError + facet_grid(rows = vars(Father.Acc))

# Pulling out degrees of freedom using Satterthwaite method (in lmerTest)

DF.Model <- lmer(MO2.NMS ~ Mass + bSpline * Offspring.Acc * Father.Acc * Mother.Acc + (1 | Father.ID) + (1 | Mother.ID) + (1 | Subject.ID) + (1 | Degree.Day), na.action = na.exclude, data = Dat)

DF <- data.frame(summary(DF.Model)$coefficients)$df
t_vals <- data.frame(summary(Model.AR)$tTab)$t.value

p_vals <- c()
for (i in 1:length(t_vals)) {
  if (t_vals[i] > 0) {
    p_vals[i] <- 2 * (pt(t_vals[i], df = DF[i], lower = FALSE))
  } else if (t_vals[i] < 0) {
    p_vals[i] <- 2 * (pt(t_vals[i], df = DF[i], lower = TRUE))
  }
}

coef_output <- data.frame(summary(Model.AR)$tTab)
coef_output$p.value <- p_vals
coef_output$DF <- DF

# Printing full model output

summary(Model.AR)

# Model output with corrected degrees of freedom and p-values

print(coef_output)
summary(ModelTMB.AR)

View(data.frame(
  "Term" = rownames(coef_output),
  "lme_Beta" = coef_output$Value, "TMB_Beta" = as.numeric(summary(ModelTMB.AR)$coefficient$cond[, 1]),
  "lme_p" = coef_output$p.value, "TMB_p" = as.numeric(summary(ModelTMB.AR)$coefficient$cond[, 4])
) %>%
  mutate("Diff" = ifelse(lme_p < 0.05 & TMB_p > 0.05, "*",
    ifelse(TMB_p < 0.05 & lme_p > 0.05, "*", " ")
  )))

# Some subtle differences between models
# Now using Kenward-Roger approximation

require(pbkrtest)

get_kr_df <- function(model_object) {
  L <- diag(rep(1, length(fixef(model_object))))
  L <- as.data.frame(L)
  out <- purrr::map_dbl(L, pbkrtest::get_Lb_ddf, object = model_object)
  names(out) <- names(fixef(model_object))
  out
}

KR_DF <- get_kr_df(DF.Model)

p_vals <- c()
for (i in 1:length(t_vals)) {
  if (t_vals[i] > 0) {
    p_vals[i] <- 2 * (pt(t_vals[i], df = as.numeric(KR_DF)[i], lower = FALSE))
  } else if (t_vals[i] < 0) {
    p_vals[i] <- 2 * (pt(t_vals[i], df = as.numeric(KR_DF)[i], lower = TRUE))
  }
}

DF_coef_output <- data.frame(summary(Model.AR)$tTab)
DF_coef_output$p.value <- p_vals
DF_coef_output$DF <- KR_DF

View(data.frame(
  "Term" = rownames(coef_output),
  "lme_BetaSat" = coef_output$Value, "lme_BetaKR" = DF_coef_output$Value,
  "TMB_Beta" = as.numeric(summary(ModelTMB.AR)$coefficient$cond[, 1]),
  "lme_pSat" = coef_output$p.value, "lme_pKR" = DF_coef_output$p.value,
  "TMB_p" = as.numeric(summary(ModelTMB.AR)$coefficient$cond[, 4])
) %>%
  mutate("Diff" = ifelse(lme_pKR < 0.05 & TMB_p > 0.05, "*",
    ifelse(TMB_p < 0.05 & lme_pKR > 0.05, "*", " ")
  )))

# Satherwaitte and KR outputs are very similar - probably owing to such large DF estimates.
# Estimating dfs according to sample sizes of offspring alone.

p_vals <- c()

for (i in 1:length(t_vals)) {
  if (t_vals[i] > 0) {
    p_vals[i] <- 2 * (pt(t_vals[i], df = 228, lower = FALSE))
  } else if (t_vals[i] < 0) {
    p_vals[i] <- 2 * (pt(t_vals[i], df = 228, lower = TRUE))
  }
}

Simple_coef_output <- data.frame(summary(Model.AR)$tTab)
Simple_coef_output$p.value <- p_vals
Simple_coef_output$DF <- 228

View(data.frame(
  "Term" = rownames(coef_output),
  "lme_Beta" = coef_output$Value,
  "TMB_Beta" = as.numeric(summary(ModelTMB.AR)$coefficient$cond[, 1]),
  "lme_pSat" = coef_output$p.value, "lme_pKR" = DF_coef_output$p.value,
  "lme_pSimple" = Simple_coef_output$p.value,
  "TMB_p" = as.numeric(summary(ModelTMB.AR)$coefficient$cond[, 4])
) %>%
  mutate("Diff" = ifelse(lme_pSimple < 0.05 & lme_pKR > 0.05, "*",
    ifelse(lme_pKR < 0.05 & lme_pSimple > 0.05, "*", " ")
  )))

# Printing off data frame

{
  T1 <- coef_output[, c("Value", "DF", "t.value", "p.value")] %>%
    mutate("Method" = "Satterthwaite", "Term" = rownames(coef_output)) %>%
    rename(
      "Test_Statistic" = "t.value", "Estimate" = "Value",
      "p" = "p.value"
    ) %>%
    select(Term, Estimate, Method, DF, Test_Statistic, p)

  T2 <- DF_coef_output[, c("Value", "DF", "t.value", "p.value")] %>%
    mutate("Method" = "Kenward-Roger", "Term" = rownames(coef_output)) %>%
    rename(
      "Test_Statistic" = "t.value", "Estimate" = "Value",
      "p" = "p.value"
    ) %>%
    select(Term, Estimate, Method, DF, Test_Statistic, p)

  T3 <- as.data.frame(summary(ModelTMB.AR)$coefficient$cond)[, c("Estimate", "z value", "Pr(>|z|)")] %>%
    mutate(
      "Method" = "z-value", "DF" = NA,
      "Term" = rownames(as.data.frame(summary(ModelTMB.AR)$coefficient$cond))
    ) %>%
    rename(
      "Test_Statistic" = "z value",
      "p" = "Pr(>|z|)"
    ) %>%
    select(Term, Estimate, Method, DF, Test_Statistic, p)

  T4 <- Simple_coef_output[, c("Value", "DF", "t.value", "p.value")] %>%
    mutate("Method" = "n-1", "Term" = rownames(coef_output)) %>%
    rename(
      "Test_Statistic" = "t.value", "Estimate" = "Value",
      "p" = "p.value"
    ) %>%
    select(Term, Estimate, Method, DF, Test_Statistic, p)
}

All <- rbind(T1, T2, T3, T4) %>%
  mutate(Method = factor(Method,
    levels = c("Satterthwaite", "Kenward-Roger", "n-1", "z-value")
  )) %>%
  arrange(Term, Method) %>%
  mutate("p < alpha" = ifelse(p < 0.05, "*", ""))

write.csv(All, "Model_Comparison_Final.csv", row.names = FALSE)

```
### Calculating marginal and conditional r-squared values
```{r warning = FALSE, message = FALSE}

r.squaredGLMM(Model.AR)

# Quite low in comparison to models in Penney et al (In Press), but somewhat reasonable.

```
### Producing marginal mean plots for lme model
```{r warning = FALSE, message = FALSE}

require("emmeans")

{
  EM_Means_Off <- emmeans::emmip(Model.AR, ~ bSpline | Offspring.Acc, cov.reduce = FALSE, nesting = NULL, nesting.order = FALSE)
  EM_Means_Mat <- emmeans::emmip(Model.AR, ~ bSpline | Mother.Acc, cov.reduce = FALSE)
  EM_Means_Pat <- emmeans::emmip(Model.AR, ~ bSpline | Father.Acc ~ bSpline, cov.reduce = FALSE)
  EM_Means_Off_Pat <- emmeans::emmip(Model.AR, Offspring.Acc ~ bSpline | Father.Acc, cov.reduce = FALSE)
  EM_Means_Off_Mat <- emmeans::emmip(Model.AR, Offspring.Acc ~ bSpline | Mother.Acc, cov.reduce = FALSE)
  EM_Means_Mass <- emmeans::emmip(Model.AR, ~Mass, at = list(Mass = seq(min(Dat$Mass, na.rm = T), max(Dat$Mass, na.rm = T), 0.1)), CIs = TRUE, type = "response", data = Dat)
}

Raw <- as.data.frame(emmeans::emmeans(Model.AR, specs = "bSpline", by = "Offspring.Acc", cov.reduce = FALSE))
bSpline_vals <- Raw$bSpline
Challenge_Temp <- c()

for (i in 1:length(bSpline_vals)) {
  Challenge_Temp[i] <- BTChallenge[c(which(BTChallenge$bSpline == bSpline_vals[i])), 9]
}

# Removing replicates

Challenge_Temp <- unique(Challenge_Temp)
EM_Off <- as.data.frame(EM_Means_Off$data)
EM_Off$Challenge <- sort(rep(Challenge_Temp, 2))

# Removing prodictions for warm acclimated offspring at cold temperatures

to_rm <- c(which(EM_Off$Offspring.Acc == "2" & EM_Off$Challenge < 19))
EM_Off <- EM_Off[-to_rm, ]
EM_Off$Upper.CI <- EM_Off$yvar + EM_Off$SE * 1.96
EM_Off$Lower.CI <- EM_Off$yvar - EM_Off$SE * 1.96

EM_Plot_Off_Ribbon <- ggplot(EM_Off, aes(x = Challenge, y = yvar, fill = Offspring.Acc, linetype = Offspring.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(fill = "Offspring Acclimation \n Temperature", linetype = "Offspring Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Mat <- as.data.frame(EM_Means_Mat$data)
EM_Mat$Challenge <- sort(rep(Challenge_Temp, 2))
EM_Mat$Upper.CI <- EM_Mat$yvar + EM_Mat$SE * 1.96
EM_Mat$Lower.CI <- EM_Mat$yvar - EM_Mat$SE * 1.96

EM_Plot_Mat_Ribbon <- ggplot(EM_Mat, aes(x = Challenge, y = yvar, linetype = Mother.Acc, fill = Mother.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(fill = "Mother Acclimation \n Temperature", linetype = "Mother Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Pat <- as.data.frame(EM_Means_Pat$data)
EM_Pat$Challenge <- sort(rep(Challenge_Temp, 2))
EM_Pat$Upper.CI <- EM_Pat$yvar + EM_Pat$SE * 1.96
EM_Pat$Lower.CI <- EM_Pat$yvar - EM_Pat$SE * 1.96

EM_Plot_Pat_Ribbon <- ggplot(EM_Pat, aes(x = Challenge, y = yvar, fill = Father.Acc, linetype = Father.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(fill = "Father Acclimation \n Temperature", linetype = "Father Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

Off_Pat <- as.data.frame(EM_Means_Off_Pat$data)
Off_Pat$Challenge <- sort(rep(Challenge_Temp, 4))
Off_Pat$Upper.CI <- Off_Pat$yvar + Off_Pat$SE * 1.96
Off_Pat$Lower.CI <- Off_Pat$yvar - Off_Pat$SE * 1.96

to_rm <- c(which(Off_Pat$Offspring.Acc == "2" & Off_Pat$Challenge < 19))
Off_Pat <- Off_Pat[-to_rm, ]

facet_names <- c(`1` = "Cold Fathers", `2` = "Warm Fathers")
facet_names_new <- c(`1` = "Cold Offspring", `2` = "Warm Offspring")

EM_Plot_Off_Pat_Ribbon <- ggplot(Off_Pat, aes(x = Challenge, y = yvar, fill = Father.Acc, linetype = Father.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(linetype = "Father Acclimation \n Temperature", fill = "Father Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  facet_wrap(~Offspring.Acc, labeller = as_labeller(facet_names_new)) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(strip.text.x = element_text(family = "Noto Sans", colour = "black"), panel.grid.major = element_blank()) +
  xlim(c(15, 30))

Off_Mat <- as.data.frame(EM_Means_Off_Mat$data)
Off_Mat$Challenge <- sort(rep(Challenge_Temp, 4))
Off_Mat$Upper.CI <- Off_Mat$yvar + Off_Mat$SE * 1.96
Off_Mat$Lower.CI <- Off_Mat$yvar - Off_Mat$SE * 1.96

to_rm <- c(which(Off_Mat$Offspring.Acc == "2" & Off_Mat$Challenge < 19))
Off_Mat <- Off_Mat[-to_rm, ]
facet_names <- c(`1` = "Cold Mothers", `2` = "Warm Mothers")

EM_Plot_Off_Mat_Ribbon <- ggplot(Off_Mat, aes(x = Challenge, y = yvar, fill = Mother.Acc, linetype = Mother.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(linetype = "Mother Acclimation \n Temperature", fill = "Mother Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  facet_wrap(~Offspring.Acc, labeller = as_labeller(facet_names_new)) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(strip.text.x = element_text(family = "Noto Sans", colour = "black"), panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Mass <- as.data.frame(EM_Means_Mass$data)
EM_Mass$Upper.CI <- EM_Mass$yvar + EM_Mass$SE * 1.96
EM_Mass$Lower.CI <- EM_Mass$yvar - EM_Mass$SE * 1.96

EM_Plot_Mass <- ggplot(EM_Mass, aes(x = Mass, y = yvar)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Mass, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  xlab("Mass (g)") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Mass (g)", y = expression("MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank())

grid.arrange(EM_Plot_Off_Ribbon, EM_Plot_Mat_Ribbon, EM_Plot_Pat_Ribbon, EM_Plot_Off_Mat_Ribbon, EM_Plot_Off_Pat_Ribbon, EM_Plot_Mass, nrow = 3)

Spline_plot <- BTChallenge %>%
  ggplot(aes(x = Challenge.Temp, y = MO2.NMS)) +
  geom_point(pch = 21, size = 3, alpha = 0.3, colour = "black", fill = "royalblue3") +
  geom_smooth(
    mapping = aes(x = Challenge.Temp, y = bSpline),
    colour = "black", linetype = "dashed"
  ) +
  labs(x = "Challenge Temperature (°C)", y = expression("MO"[2] * " (mg O"[2] * "/h)")) +
  theme_bw() +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans"))

print(Spline_plot)

# Producing plots to save

dev.new()
EM_Plot_Off_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Offspring_alone.jpeg", EM_Plot_Off_Ribbon, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Mat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Mothers_alone.jpeg", EM_Plot_Mat_Ribbon, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Pat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Fathers_alone.jpeg", EM_Plot_Pat_Ribbon, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Off_Mat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Offspring_by_mothers.jpeg", EM_Plot_Off_Mat_Ribbon, dpi = 800, width = 10, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Off_Pat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Offspring_by_fathers.jpeg", EM_Plot_Off_Pat_Ribbon, dpi = 800, width = 10, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Mass
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Mass_alone.jpeg", EM_Plot_Mass, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
Spline_plot
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Spline_plot.jpeg", Spline_plot, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

## With dots

EM_Plot_Off_Ribbon <- ggplot(EM_Off, aes(x = Challenge, y = yvar, fill = Offspring.Acc, linetype = Offspring.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  labs(fill = "Offspring Acclimation \n Temperature", linetype = "Offspring Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30)) +
  stat_summary(geom = "point", fun = "mean", size = 2, colour = "black", pch = 21, alpha = 0.2, data = Dat, aes(x = Challenge.Temp, y = MO2.NMS))

EM_Plot_Mat_Ribbon <- ggplot(EM_Mat, aes(x = Challenge, y = yvar, colour = Mother.Acc, fill = Mother.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE) +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_colour_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  labs(fill = "Mother Acclimation \n Temperature", colour = "Mother Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30)) +
  stat_summary(geom = "point", fun = "mean", size = 2, colour = "black", pch = 21, alpha = 0.2, data = Dat, aes(x = Challenge.Temp, y = MO2.NMS))

EM_Plot_Pat_Ribbon <- ggplot(EM_Pat, aes(x = Challenge, y = yvar, fill = Father.Acc, colour = Father.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE) +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_colour_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  labs(fill = "Father Acclimation \n Temperature", colour = "Father Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

facet_names <- c(`1` = "Cold Fathers", `2` = "Warm Fathers")
facet_names_new <- c(`1` = "Cold Offspring", `2` = "Warm Offspring")

EM_Plot_Off_Pat_Ribbon <- ggplot(Off_Pat, aes(x = Challenge, y = yvar, fill = Father.Acc, colour = Father.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE) +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_colour_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  labs(colour = "Father Acclimation \n Temperature", fill = "Father Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  facet_wrap(~Offspring.Acc, labeller = as_labeller(facet_names_new)) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(strip.text.x = element_text(family = "Noto Sans", colour = "black"), panel.grid.major = element_blank()) +
  xlim(c(15, 30))

facet_names <- c(`1` = "Cold Mothers", `2` = "Warm Mothers")

EM_Plot_Off_Mat_Ribbon <- ggplot(Off_Mat, aes(x = Challenge, y = yvar, fill = Mother.Acc, colour = Mother.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE) +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_colour_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  labs(colour = "Mother Acclimation \n Temperature", fill = "Mother Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  facet_wrap(~Offspring.Acc, labeller = as_labeller(facet_names_new)) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(strip.text.x = element_text(family = "Noto Sans", colour = "black"), panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Plot_Mass <- ggplot(EM_Mass, aes(x = Mass, y = yvar)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Mass, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  xlab("Mass (g)") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Mass (g)", y = expression("MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank())

```
### Producing marginal mean plots for glmmTMB model
```{r warning = FALSE, message = FALSE}

{
  EM_Means_Off <- emmeans::emmip(ModelTMB.AR, Offspring.Acc ~ bSpline, cov.reduce = FALSE)
  EM_Means_Mat <- emmeans::emmip(ModelTMB.AR, Mother.Acc ~ bSpline, cov.reduce = FALSE)
  EM_Means_Pat <- emmeans::emmip(ModelTMB.AR, Father.Acc ~ bSpline, cov.reduce = FALSE)
  EM_Means_Off_Pat <- emmeans::emmip(ModelTMB.AR, Offspring.Acc ~ bSpline | Father.Acc, cov.reduce = FALSE)
  EM_Means_Off_Mat <- emmeans::emmip(ModelTMB.AR, Offspring.Acc ~ bSpline | Mother.Acc, cov.reduce = FALSE)
  EM_Means_Mass <- emmeans::emmip(ModelTMB.AR, ~Mass, at = list(Mass = seq(min(Dat$Mass, na.rm = T), max(Dat$Mass, na.rm = T), 0.1)), CIs = TRUE, type = "response", data = Dat)
}

Raw <- as.data.frame(emmeans::emmeans(ModelTMB.AR, specs = "bSpline", by = "Offspring.Acc", cov.reduce = FALSE))
bSpline_vals <- Raw$bSpline

Challenge_Temp <- c()
for (i in 1:length(bSpline_vals)) {
  Challenge_Temp[i] <- BTChallenge[c(which(BTChallenge$bSpline == bSpline_vals[i])), 9]
}

# Removing replicates again

Challenge_Temp <- unique(Challenge_Temp)
EM_Off <- as.data.frame(EM_Means_Off$data)
EM_Off$Challenge <- sort(rep(Challenge_Temp, 2))

# Removing prodictions for warm acclimated offspring at cold temperatures

to_rm <- c(which(EM_Off$Offspring.Acc == "2" & EM_Off$Challenge < 19))
EM_Off <- EM_Off[-to_rm, ]
EM_Off$Upper.CI <- EM_Off$yvar + EM_Off$SE * 1.96
EM_Off$Lower.CI <- EM_Off$yvar - EM_Off$SE * 1.96

EM_Plot_Off_Ribbon <- ggplot(EM_Off, aes(x = Challenge, y = yvar, fill = Offspring.Acc, linetype = Offspring.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(fill = "Offspring Acclimation \n Temperature", linetype = "Offspring Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Mat <- as.data.frame(EM_Means_Mat$data)
EM_Mat$Challenge <- sort(rep(Challenge_Temp, 2))
EM_Mat$Upper.CI <- EM_Mat$yvar + EM_Mat$SE * 1.96
EM_Mat$Lower.CI <- EM_Mat$yvar - EM_Mat$SE * 1.96

EM_Plot_Mat_Ribbon <- ggplot(EM_Mat, aes(x = Challenge, y = yvar, linetype = Mother.Acc, fill = Mother.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(fill = "Mother Acclimation \n Temperature", linetype = "Mother Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Pat <- as.data.frame(EM_Means_Pat$data)
EM_Pat$Challenge <- sort(rep(Challenge_Temp, 2))
EM_Pat$Upper.CI <- EM_Pat$yvar + EM_Pat$SE * 1.96
EM_Pat$Lower.CI <- EM_Pat$yvar - EM_Pat$SE * 1.96

EM_Plot_Pat_Ribbon <- ggplot(EM_Pat, aes(x = Challenge, y = yvar, fill = Father.Acc, linetype = Father.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(fill = "Father Acclimation \n Temperature", linetype = "Father Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank()) +
  xlim(c(15, 30))

Off_Pat <- as.data.frame(EM_Means_Off_Pat$data)
Off_Pat$Challenge <- sort(rep(Challenge_Temp, 4))
Off_Pat$Upper.CI <- Off_Pat$yvar + Off_Pat$SE * 1.96
Off_Pat$Lower.CI <- Off_Pat$yvar - Off_Pat$SE * 1.96

to_rm <- c(which(Off_Pat$Offspring.Acc == "2" & Off_Pat$Challenge < 19))
Off_Pat <- Off_Pat[-to_rm, ]

facet_names <- c(`1` = "Cold Fathers", `2` = "Warm Fathers")
facet_names_new <- c(`1` = "Cold Offspring", `2` = "Warm Offspring")

EM_Plot_Off_Pat_Ribbon <- ggplot(Off_Pat, aes(x = Challenge, y = yvar, fill = Father.Acc, linetype = Father.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(linetype = "Father Acclimation \n Temperature", fill = "Father Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  facet_wrap(~Offspring.Acc, labeller = as_labeller(facet_names_new)) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(strip.text.x = element_text(family = "Noto Sans", colour = "black"), panel.grid.major = element_blank()) +
  xlim(c(15, 30))

Off_Mat <- as.data.frame(EM_Means_Off_Mat$data)
Off_Mat$Challenge <- sort(rep(Challenge_Temp, 4))
Off_Mat$Upper.CI <- Off_Mat$yvar + Off_Mat$SE * 1.96
Off_Mat$Lower.CI <- Off_Mat$yvar - Off_Mat$SE * 1.96

to_rm <- c(which(Off_Mat$Offspring.Acc == "2" & Off_Mat$Challenge < 19))
Off_Mat <- Off_Mat[-to_rm, ]

facet_names <- c(`1` = "Cold Mothers", `2` = "Warm Mothers")

EM_Plot_Off_Mat_Ribbon <- ggplot(Off_Mat, aes(x = Challenge, y = yvar, fill = Mother.Acc, linetype = Mother.Acc)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Challenge, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  scale_fill_manual(values = c("dodgerblue3", "magenta"), labels = c("Cold", "Warm")) +
  scale_linetype_manual(values = c("solid", "dashed"), labels = c("Cold", "Warm")) +
  labs(linetype = "Mother Acclimation \n Temperature", fill = "Mother Acclimation \n Temperature") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  facet_wrap(~Offspring.Acc, labeller = as_labeller(facet_names_new)) +
  labs(x = "Challenge Temperature (°C)", y = expression("Resting MO"[2] * " (mg O"[2] * "/h)")) +
  theme(strip.text.x = element_text(family = "Noto Sans", colour = "black"), panel.grid.major = element_blank()) +
  xlim(c(15, 30))

EM_Mass <- as.data.frame(EM_Means_Mass$data)
EM_Mass$Upper.CI <- EM_Mass$yvar + EM_Mass$SE * 1.96
EM_Mass$Lower.CI <- EM_Mass$yvar - EM_Mass$SE * 1.96

EM_Plot_Mass <- ggplot(EM_Mass, aes(x = Mass, y = yvar)) +
  theme_bw() +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 7, bs = "cs"), se = FALSE, colour = "black") +
  geom_ribbon(mapping = aes(x = Mass, ymin = c(Lower.CI), ymax = c(Upper.CI)), alpha = 0.3, colour = NA) +
  xlab("Mass (g)") +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans")) +
  labs(x = "Mass (g)", y = expression("MO"[2] * " (mg O"[2] * "/h)")) +
  theme(panel.grid.major = element_blank())

grid.arrange(EM_Plot_Off_Ribbon, EM_Plot_Mat_Ribbon, EM_Plot_Pat_Ribbon, EM_Plot_Off_Mat_Ribbon, EM_Plot_Off_Pat_Ribbon, EM_Plot_Mass, nrow = 3)

Spline_plot <- BTChallenge %>%
  ggplot(aes(x = Challenge.Temp, y = MO2.NMS)) +
  geom_point(pch = 21, size = 3, alpha = 0.3, colour = "black", fill = "royalblue3") +
  geom_smooth(
    mapping = aes(x = Challenge.Temp, y = bSpline),
    colour = "black", linetype = "dashed"
  ) +
  labs(x = "Challenge Temperature (°C)", y = expression("MO"[2] * " (mg O"[2] * "/h)")) +
  theme_bw() +
  theme(axis.text = element_text(size = 8, colour = "black", family = "Noto Sans"))

print(Spline_plot)

dev.new()
EM_Plot_Off_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Offspring_alone_z.jpeg", EM_Plot_Off_Ribbon, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Mat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Mothers_alone_z.jpeg", EM_Plot_Mat_Ribbon, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Pat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Fathers_alone_z.jpeg", EM_Plot_Pat_Ribbon, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Off_Mat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Offspring_by_mothers_z.jpeg", EM_Plot_Off_Mat_Ribbon, dpi = 800, width = 10, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Off_Pat_Ribbon
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Offspring_by_fathers_z.jpeg", EM_Plot_Off_Pat_Ribbon, dpi = 800, width = 10, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
EM_Plot_Mass
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Mass_alone_z.jpeg", EM_Plot_Mass, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

dev.new()
Spline_plot
showtext_opts(dpi = 800)
showtext_auto()
ggsave("/home/joshk/Documents/Trout/Brook Trout Challenge Data/Spline_z.jpeg", Spline_plot, dpi = 800, width = 9.45, height = 6.72)
showtext_auto(enable = FALSE)

```
